\documentclass[aspectratio=169]{beamer}

\usetheme{Madrid}
\usecolortheme{default}
\setbeamertemplate{navigation symbols}{}

\title{My Research Direction and Interests}
\subtitle{A One-Minute Introduction}
\author{Rose (Jibao Yuan)}
\institute{National University of Defense Technology}
\date{April 2026}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Who I Am}
  \begin{itemize}
    \item I am a first-year Master's student in Electronic Information at NUDT.
    \item I received my B.Eng. in Artificial Intelligence from South China Normal University.
    \item My academic background is in reinforcement learning, and now I am moving toward embodied intelligence.
  \end{itemize}
\end{frame}

\begin{frame}{My Research Direction}
  \begin{itemize}
    \item My earlier work focused on Multi-Agent Reinforcement Learning, especially cooperative learning methods.
    \item Now I am shifting my main focus to Embodied AI, because I want to study systems that can work in the physical world.
    \item I am especially interested in closing the sim-to-real gap for robot learning.
  \end{itemize}
\end{frame}

\begin{frame}{My Research Interests}
  \begin{block}{Topics I want to explore}
    \begin{itemize}
      \item Robotic manipulation, grasping, and dexterous control
      \item Vision-Language-Action models for general-purpose robots
      \item Scalable data and training pipelines for embodied intelligence
    \end{itemize}
  \end{block}

  \vspace{0.4em}
  \textbf{Goal:} to build intelligent agents that can perceive, decide, and act more effectively in real environments.
\end{frame}

\end{document}
